---
title: "Dat 605 - HW7 - Week 7, Imp. Distributions / EX / VARX"
author: "sufian"
date: "2/22/2020"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Types of Probability Distribution Exercise


```{r, message=FALSE, warning=FALSE}
library(matlib)
library(MASS)
```

------------------------------------------------------------------------------------------------------------------

\clearpage

## Prob 1


Let Y = min(X1,X2,X3,X4....Xn)

Also let F(y) be the CDF:

F(y) = P(Y≤y)

     = 1 - P(Y<y)
     
     = 1 - P(X1>y, X2>y, X3>y,...........Xn>y)
     
     = 1 - P(X1>y)*P(X2>y)*P(X3>y)....*P(Xn>y)
     
     = 1 - F(x1)*F(x2)*F(x3)*...........*F(xn)
       
Therefore, F(y) = 1 - [$\frac{1}{k}$*$\frac{1}{k}$*$\frac{1}{k}$....$\frac{1}{k^n}$]

or F(y) = 1 - $\frac{1}{k^n}$ is the distribution for integer 1 to k


------------------------------------------------------------------------------------------------------------------

\clearpage


## Prob 2a

- Geometric Distribution formula:

Pr(X=k) = $(1-p)^{k}$ p

for k = 0, 1, 2, 3, 4.....

In our case, p is the first time machine breaks down =>1/10
Therefore In this case, the success of the event signifies the failure of a machine

```{r}
p <- 1/10
q <- 1-p

Pr8 <- q^8 # k= 8 because we are looking for not failing in the frist 8 yrs
print("Prob will fail after 8 yrs")
print(round(Pr8,7))
print("Expected value :")
print(E <- 1/p)
print("Std Dev :")
print(stddev<-sqrt((1-p)/p^2))
```
## Prob 2b

- Exponential Distribution formula:

f(X=k) = exp$\lambda$(-x) for x >= 0 and is zero for x < 0


```{r}
lambda <- 1/10
x <-8 #after 8 years 

fx <- exp(-lambda*x) # for x >= 8 years
print('Prob will fail after 8 yrs')
print(fx)

print("Expected value :")
print(E<-1/lambda)

print("Std Dev :")
print(E<-sqrt(1/(lambda^2)))
```

## Prob 2c

- Binomial Distribution formula:

Pr(X=k) = $\binom{n}{k}$$p^{k}$$(1-p)^{n-k}$  for k = 0,1,2...

whereby, $\binom{n}{k}$ = $\frac{n!}{(n-k)!k!}$ 

```{r}
n <-8 # The numuber of years where there's no failures
k <-0 # Here K is the number of failure occurances (or zero sucesses)
p <-1/10 # Probability of failing in 10 years


Prbinomial <- choose(n,k)*p^k*(1-p)^(n-k)
print('Prob will fail after 8 yrs')
print(Prbinomial)

Ebinomial <- n*p
Varbinomial <- n*p*(1-p)
print("Expected Value :")
print(Ebinomial)

print("Std. Dev :")
print(sqrt(Varbinomial))

```

## Prob 2d

- Poisson Distribution formula:

Pr(X=k) =  $\lambda$exp(-$\lambda$)/k!  for k = 0,1,2...to infinity

```{r}
lambdap <- .8 #here avg rate of "success" = rate of failures in 8 years was scaled from 1 out of 10 years
k <- 0 #zero "success" =  zero "machine failures"
Prpoission <- ((lambdap^k)*exp(-lambdap))/factorial(k)
print('Prob will fail after 8 yrs')
print(Prpoission)

Epoission <- lambdap
print("Expected Value :")
print(Epoission)
Varpoission <- lambdap
print("Std. Dev :")
print(sqrt(Varpoission))
```

