---
title: "Dat 605 HW 4 - SVD Decomposition Exercise"
author: "sufian"
date: "2/13/2020"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prob Set 1

- SVD Decomposition Step by Step

```{r message=FALSE, warning=FALSE}

library(matlib)
library(MASS)

```

## Setting up A mxn Matrix

- X = AAT

- Y = ATA

```{r}
A <- matrix(c(1, 2, 3, -1,0,4), nrow = 2, ncol = 3, byrow=T)

A

```


```{r}

X <- A%*%t(A) #AAT

X

Y <- t(A)%*%A #ATA

Y
```

- Eigenvectors of ATA matrix


```{r}
Y.e <- eigen(Y) #eigen of ATA

values.mat <-Y.e$values
values.mat #this will show that the last eignevalue is virtually zero

vector.mat <- Y.e$vectors #eignen vectors of ATA

#vector.mat[,1:2] <- vector.mat[,1:2]*-1

vector.moat <- vector.mat[,1:2]

vector.moat

```

- Performing the same routine for AAT; X Matrix

```{r}

X.e <- eigen(X) #eigen of AAT

uvalues.mat <- X.e$values #eigen values of AAT
uvector.mat <- X.e$vectors #eigen vectors of AAT

uvector.mat

```

- The singular values r are the square roots of the non-zero eigenvalues of the AAT and ATA matrices


```{r}
r <- sqrt(Y.e$values)

r <- r*diag(length(r))[,1:2]

r <-r[1:2,]

r
```


------------------------------------------------------------------------------------------------------------------

\clearpage

- The manual step by step process aligns with the output of the svd() function below. 

- We can also show that the matrix A is indeed equal to the components resulting from singular value decomposition.

------------------------------------------------------------------------------------------------------------------

\clearpage

```{r}
svd.matrix <- uvector.mat %*% r %*% t(vector.moat)
svd.matrix # this results the same as the original A matrix we began with
```

## Confirmation with R built-in function below:

- The singular value decomposition of the matrix is computed using the R svd() function

```{r}
A.svd <- svd(A)
A.svd
```

## Prob Set 2

- Inverse of a Matrix using R built-in cofactor functions

```{r}


myinverse <- function(A1,n){
  
# Pre-populate nxn matrix with zeros
  nrow <- n
  ncol <- n

#create place-holder C matrix of zeros
C <- matrix(0, nrow = n, ncol = n)
  
i <-1
#j<-1
while (i < n+1){
 for (j in 1:n) {
  C[i,j]<- cofactor(A1, i,j)
 }
  i<-i+1
}
#Matrix of Co-factors of original Matrix A
C
#transpose of Cofactor Matrix
print("Cofactors of Matrix A :")
Ctranspose <- t(C)

print(Ctranspose)

#Determinant of original Matrix A
print("The Determinant of Matrix A :")
Det_A1 <- det(A1)
print(Det_A1)

#Inverse of original Matrix A
print("The Inverse of A is :")

A_Inv <- Ctranspose/Det_A1
print(A_Inv)

print("To verify that AxA(inverse) = Identity :")
I <- A1 %*% A_Inv

return (I)  
}

```


## Test the Function out; Driver Matrix A1

```{r}

n<-3

A1 <- matrix(c(1,2,3,0,1,4,5,6,0),nrow=3,ncol=3, byrow=T)
print("Original Matrix of A :")
A1
myinverse(A1,n)

```




